Fast and exact visibility on digitized shapes and application to saliency-aware normal estimation

### 2025-04-25 DGMM2025/computation.tex
Working on 3

\begin{figure}
  \begin{tikzpicture}
    \centering
    \begin{axis}[
        width=0.8\textwidth,
        legend columns=3,
        xlabel={Gridstep},
        ylabel={Mean distance},
        x dir=reverse,
        legend pos=north west,
        ymajorgrids=true,
        grid style=dashed,
        ymax=70,
        ymode=log,
        xmode=log,
        log ticks with fixed point,
      ]

      \addplot[
        color=cyan,
      ] coordinates {
        (0.0625,7.61948)(0.125,5.49755)(0.25,3.97418)(0.375,3.00921)(0.5,2.85702)(0.625,2.34448)(0.75,1.85023)(0.875,2.16868)(1.0,1.85023)
      };
      \addlegendentry{sphere1}
      \addplot[
        color=red,
      ] coordinates {
        (0.0625,38.1045)(0.125,26.8765)(0.25,19.6747)(0.375,16.6192)(0.5,14.0867)(0.625,12.5062)(0.75,11.3734)(0.875,10.2845)(1,8.90781)
      };
      \addlegendentry{goursat}
      \addplot[
        color=violet,
      ] coordinates {
        (0.0625,25.5024)(0.125,18.2364)(0.25,12.3975)(0.375,9.41303)(0.5,8.69558)(0.625,7.37667)(0.75,6.82131)(0.875,6.05735)(1,6.33877)
      };
      \addlegendentry{torus}
      \addplot[
        color=MyGreen,
      ] coordinates {
        (0.0625,27.9287)(0.125,17.5104)(0.25,10.8007)(0.375,8.69514)(0.5,7.26074)(0.625,6.2309)(0.75,5.6897)(0.875,5.28197)(1,4.96098)
      };
      \addlegendentry{leopold}
      \addplot[
        color=yellow!80!black,
      ] coordinates {
        (0.0625,41.9816)(0.125,27.7104)(0.25,18.2339)(0.375,14.6475)(0.5,12.3618)(0.625,9.55647)(0.75,9.83208)(0.875,7.51861)(1,7.99732)
      };
      \addlegendentry{rcube}
      \addplot [
        color=black,
        thick,
        domain=0.0625:1,
        samples=100,
      ] {x^(-0.5)};
      \addlegendentry{$\sqrt{h}=\sqrt{\frac{1}{x}}$}
    \end{axis}
  \end{tikzpicture}
  \caption{Mean Visibility Distance as a Function of Grid Resolution}
  \label{fig:meanvisibility-gridstep}
\end{figure}

\begin{figure}[t]
  \input{pointelscomptime.tikz}
  \caption{Computation time of visibility as a function of the number
    of pointels. We compare the computation time of the naive breadth
    first visibility algorithm against our algorithm using
    intervals. We input the same maximal radius to both versions (10,
    20, 30) and test it on 6 different figures (goursat, torus, rcube,
    sphere9, leopold, d20) with various gridsteps, giving us figures
    with pointel amounts ranging from 520 to 390235.}
  \label{fig:meanvisibility-computationComplexity}
\end{figure}

>>>>

\begin{figure}[t]
  \input{pointelscomptime.tikz}
  \caption{ \label{fig:meanvisibility-computationComplexity}Computation
    time of visibility as a function of the number of pointels. We
    compare the computation time of the naive breadth first visibility
    algorithm against our algorithm using intervals. We input the same
    maximal radius to both versions (10, 20, 30) and test it on 6
    different figures (goursat, torus, rcube, sphere9, leopold, d20)
    with various gridsteps, giving us figures with pointel amounts
    ranging from 520 to 390235.}
\end{figure}

\begin{figure}
  \input{mean-distance.tikz}
  \caption{  \label{fig:meanvisibility-gridstep}. Mean Visibility Distance as a Function of Grid Resolution}
\end{figure}
